Mike's Scratchpad for DATA 621 Homework #4

### 2019-11-09 hw4/HW4_Mike.Rmd
Updated Mike's scratchpad

temp <- df %>%
  rowwise() %>%
  mutate(INCOME = strip_dollars(INCOME),
         HOME_VAL = strip_dollars(HOME_VAL),
         BLUEBOOK = strip_dollars(BLUEBOOK),
         OLDCLAIM = strip_dollars(OLDCLAIM)) %>%
  mutate(JOB = ifelse(str_length(JOB) > 0, JOB, NA),
         CAR_AGE = ifelse(str_length(CAR_AGE) > 0, CAR_AGE, NA),
         EDUCATION = ifelse(EDUCATION == "<High_School", "LT_High_School", EDUCATION),
         URBANICITY = ifelse(URBANICITY == "Highly Urban/ Urban", "Urban", "Rural")) %>%
  mutate(DRIVER_TYPE = get_driver_type(SEX, AGE)) %>%
  ungroup() %>%
  na.omit() %>%
  to_dummies("PARENT1", T) %>%
  to_dummies("KIDSDRIV", T) %>%
  to_dummies("HOMEKIDS", T) %>%
  to_dummies("MSTATUS", T) %>%
  to_dummies("SEX", T) %>%
  to_dummies("EDUCATION", T) %>%
  to_dummies("JOB", T) %>%
  to_dummies("CAR_USE", T) %>%
  to_dummies("CAR_TYPE", T) %>%
  to_dummies("RED_CAR", T) %>%
  to_dummies("REVOKED", T) %>%
  to_dummies("MVR_PTS", T) %>%
  to_dummies("URBANICITY", T) %>%
  to_dummies("DRIVER_TYPE", T) %>%
  rowwise() %>%
  mutate(BLUEBOOK = ifelse(BLUEBOOK > 0, BLUEBOOK, 0)) %>%
  # mutate(LOG10_INCOME = log10(INCOME + 1),
  #        LN_INCOME = log(INCOME + 1),
  #        LOG10_HOME_VAL = log10(HOME_VAL + 1),
  #        LN_HOME_VAL = log(HOME_VAL + 1),
  #        LOG10_BLUEBOOK = log10(BLUEBOOK + 1),
  #        LN_BLUEBOOK = log(BLUEBOOK + 1),
  #        LOG10_OLDCLAIM = log10(OLDCLAIM + 1),
  #        LN_OLDCLAIM = log(OLDCLAIM + 1)) %>%
  mutate(PRIOR_CLAIM = ifelse(CLM_FREQ + OLDCLAIM > 0, 1,0)) %>%
  ungroup() 
```

```{r}
set.seed(42)
minority <- nrow(temp[temp$TARGET_FLAG == 1,])
majority <- nrow(temp[temp$TARGET_FLAG == 0,])
diff <- majority - minority
minority_index <- temp[temp$TARGET_FLAG == 1,]$INDEX
over_sample_df <- data.frame(INDEX = sample(minority_index, diff, T)) %>%
  merge(temp, .) %>%
  bind_rows(temp)

train_index <- createDataPartition(over_sample_df$TARGET_FLAG, p = .7, list = FALSE, times = 1)
train <- over_sample_df[train_index,]
test <- over_sample_df[-train_index,]
```

```{r}
fft_train <- train %>%
  select(-TARGET_AMT, -INDEX)#, -OLDCLAIM, -CLM_FREQ)
fft_test <- test %>%
  select(-TARGET_AMT, -INDEX)#, -OLDCLAIM, -CLM_FREQ)
fit <- FFTrees(TARGET_FLAG ~ ., fft_train, fft_test)
plot(fit)
```
The FFTree suggests that past history of filing claims is a good predictor if someone will file a claim in the future.  This could be our baseline model criteria.

>>>>

temp <- df %>%
  rowwise() %>%
  mutate(INCOME = strip_dollars(INCOME),
         HOME_VAL = strip_dollars(HOME_VAL),
         BLUEBOOK = strip_dollars(BLUEBOOK),
         OLDCLAIM = strip_dollars(OLDCLAIM)) %>%
  mutate(JOB = ifelse(str_length(JOB) > 0, JOB, NA),
         CAR_AGE = ifelse(str_length(CAR_AGE) > 0, CAR_AGE, NA),
         EDUCATION = ifelse(EDUCATION == "<High_School", "LT_High_School", EDUCATION),
         URBANICITY = ifelse(URBANICITY == "Highly Urban/ Urban", "Urban", "Rural")) %>%
  mutate(DRIVER_TYPE = get_driver_type(SEX, AGE)) %>%
  ungroup() %>%
  na.omit() %>%
  to_dummies("PARENT1", T) %>%
  to_dummies("KIDSDRIV", T) %>%
  to_dummies("HOMEKIDS", T) %>%
  to_dummies("MSTATUS", T) %>%
  to_dummies("SEX", T) %>%
  to_dummies("EDUCATION", T) %>%
  to_dummies("JOB", T) %>%
  to_dummies("CAR_USE", T) %>%
  to_dummies("CAR_TYPE", T) %>%
  to_dummies("RED_CAR", T) %>%
  to_dummies("REVOKED", T) %>%
  to_dummies("MVR_PTS", T) %>%
  to_dummies("URBANICITY", T) %>%
  to_dummies("DRIVER_TYPE", T) %>%
  rowwise() %>%
  mutate(BLUEBOOK = ifelse(BLUEBOOK > 0, BLUEBOOK, 0)) %>%
  # mutate(LOG10_INCOME = log10(INCOME + 1),
  #        LN_INCOME = log(INCOME + 1),
  #        LOG10_HOME_VAL = log10(HOME_VAL + 1),
  #        LN_HOME_VAL = log(HOME_VAL + 1),
  #        LOG10_BLUEBOOK = log10(BLUEBOOK + 1),
  #        LN_BLUEBOOK = log(BLUEBOOK + 1),
  #        LOG10_OLDCLAIM = log10(OLDCLAIM + 1),
  #        LN_OLDCLAIM = log(OLDCLAIM + 1)) %>%
  #mutate(PRIOR_CLAIM = ifelse(CLM_FREQ + OLDCLAIM > 0, 1,0)) %>%
  ungroup()

set.seed(42)
# Split the data
train_index <- createDataPartition(temp$TARGET_FLAG, p = .7, list = FALSE, times = 1)
train <- temp[train_index,]
test <- temp[-train_index,]

# Ballance the data
minority <- nrow(train[train$TARGET_FLAG == 1,])
majority <- nrow(train[train$TARGET_FLAG == 0,])
diff <- majority - minority
minority_index <- train[train$TARGET_FLAG == 1,]$INDEX
over_sample_df <- data.frame(INDEX = sample(minority_index, diff, T)) %>%
  merge(train, .) %>%
  bind_rows(train)
```

```{r}
set.seed(42)
fft_train <- over_sample_df %>%
  select(-TARGET_AMT, -INDEX)#, -OLDCLAIM, -CLM_FREQ)
fft_test <- test %>%
  select(-TARGET_AMT, -INDEX)#, -OLDCLAIM, -CLM_FREQ)
fit <- FFTrees(TARGET_FLAG ~ ., fft_train, fft_test, do.comp = FALSE)
plot(fit)
plot(fit, data="test")

test_results = data.frame(yhat = ifelse(predict(fit, test),1,0), TARGET_FLAG = test$TARGET_FLAG)
table(test_results$yhat, test_results$TARGET_FLAG)
```
The FFTree suggests that past history of filing claims is a good predictor if someone will file a claim in the future.  This could be our baseline model criteria.
